Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985 - Article codes, models, and figures for replication

### 2023-08-16 Article code, models, and figures/Which Amazon Problem article codes, models, and figures.Rmd
Added latest updates to figures

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

```{r Figure pure, fig.cap="Pure-types constructions in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
#summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat != "Other",
     	mx_cat != "Mixed-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
          	se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of pure-types problem-constructions by year",
   	subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
   	caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  theme(legend.position = "bottom") +
  scale_color_discrete(labels = c("Economic Integration", "Environmental Conservation",
                              	"Social Development", "National Sovereignty"))+
  guides(color=guide_legend(nrow=2,byrow=TRUE))
```

@@

```{r peak years test, fig.cap="Lag analysis for problem-constructions and for year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_mx %>%
  count(year, mx_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n),
         year = lubridate::as_date(year)) %>% 
  select(-n) %>%
  filter(mx_cat != "Other") %>%
  group_by(mx_cat) %>% 
  plot_acf_diagnostics(.date_var = year,
                       .value = perc,
                       .show_white_noise_bars = TRUE,
                       .interactive = FALSE)
```

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(ggplot2)
library(plm)
library(timetk)
library(lubridate)
library(geomtextpath)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

```{r Figure pure, echo=FALSE, fig.cap="Pure-types constructions in time", message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
#summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat != "Other",
     	mx_cat != "Mixed-types") %>%
  mutate(mx_cat=case_when(
    mx_cat== "Pure Economic Integration" ~"Economic Integration",
    mx_cat== "Pure National Sovereignty" ~"National Sovereignty",
    mx_cat== "Pure Social Development"~"Social Development",
    mx_cat== "Pure Environmental Conservation"~"Environmental Conservation"))%>%
  ggplot(aes(x=as.numeric(year), y = perc, color = mx_cat)) +
  geom_textsmooth(aes(label=mx_cat,hjust=mx_cat), fontface="bold", size=4)+
  scale_hjust_manual(values=c(0.075,0.075,.5,.5))+
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of pure-types problem-constructions by year",
   	subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
   	caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  theme(legend.position = "none") +
  scale_color_discrete(labels = c("Economic Integration", "Environmental Conservation",
                              	"Social Development", "National Sovereignty"))+
  guides(color=guide_legend(nrow=2,byrow=TRUE))
```

@@

```{r peak years test, fig.cap="Lag analysis for problem-constructions and for year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_mx %>%
  count(year, mx_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n),
         year = lubridate::as_date(year)) %>% 
  select(-n) %>%
  filter(mx_cat != "Other") %>%
  group_by(mx_cat) %>%
  mutate(mx_cat=case_when(
    mx_cat== "Pure Economic Integration" ~"Economic Integration",
    mx_cat== "Pure National Sovereignty" ~"National Sovereignty",
    mx_cat== "Pure Social Development"~"Social Development",
    mx_cat== "Pure Environmental Conservation"~"Environmental Conservation"))%>%
  drop_na(mx_cat) %>%
  plot_acf_diagnostics(.date_var = year,
                       .value = perc,
                       .show_white_noise_bars = TRUE,
                       .interactive = FALSE)
```
